---
title: "RStudio2"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 2.1

```{r include=FALSE}
set.seed(2017556451)
library(tidyverse)
library(knitr)
data<-read_csv("RStudio2_data.csv")

newdata<- data[sample(nrow(data),size = 100),ncol=5]

```

### 1.Calculate the mean sales’ values for each color.

```{r echo=FALSE}
one<-newdata %>%
  group_by(Color) %>%
  summarise(avg_sales = mean(Sales))
kable(one)
```

### 2. Calculate the mean sales’ values for each region.
```{r echo=FALSE}
two<-newdata %>%
  group_by(Region) %>%
  summarise(avg_sales = mean(Sales))
kable(two)

```

### 3.Identify the five highest sales’ value according to date, color and region separately.

```{r echo=FALSE}
 three<-newdata %>%
  group_by(Date) %>%
  summarise(Sales = max(Sales)) %>%
  arrange(desc(Sales)) %>%
  head(5)
  kable(three)
  
  four<-newdata %>%
  group_by(Color,Sales) %>%
  summarise(Sales = max(Sales)) %>%
  arrange(desc(Sales)) %>%
  head(5)
  kable(four)
  
  five<-newdata %>%
  group_by(Region,Sales) %>%
  summarise(Sales = max(Sales)) %>%
  arrange(desc(Sales)) %>%
  head(5)
  kable(five)
```

### 4.Identify the month in which the mean sales’ value is the highest.

```{r include=FALSE}
six <- newdata %>%
  separate(Date,into = c("Day","Month","Year"),sep = "-" )


seven<-six %>%
  group_by(Month) %>%
  summarise(Sales = mean(Sales)) %>%
  arrange(desc(Sales)) %>%
  head(1)
```

The month with the highest sales is `r seven`

### 5.Plot the sales according to years.

```{r echo=FALSE}
ggplot(data = six, aes(x=Year,y=Sales)) +
  geom_bar(stat="identity",width = 0.3,fill = "pink")
```

## Assignment 2.2

```{r include=FALSE}
set.seed(2017556451)
words<-stringr::words
```

### 1.Take a sample of 100 words from this data, and save this sample as a new data
  
```{r echo=FALSE}
newdata <- sample(words,100)
kable(newdata)
```

### 2.Find words which are starting with “a” and ending with “e”.

```{r include=FALSE}
start <- str_subset(newdata,"^a") 
end <- str_subset(start,"e$")
```
Words are starting with “a” and ending with “e” `r end`

## 3.Calculate the number of words which have more than 3 vowels.

```{r echo=FALSE}
wovels <- str_count(newdata,"[aeiou]") 
sumwovels<-sum(wovels > 3)
```

number of words which have more than 3 vowels is `r sumwovels`.

### 4.List the five longest word in your data

```{r echo=FALSE}
 eight <-str_length(newdata)
mydata<- tibble(
   word = newdata,
   num = eight,
 )
  list<- mydata %>% 
   group_by(word) %>% 
   arrange(desc(num)) %>%
   head(5)
 kable(list)
```

### 5.Try to find word(s) which contain any of these words: age, any, day, exp, her, pro, the.

```{r echo=FALSE}
sample<-c("age","any","day","exp","her","pro")
match<-str_c(sample,collapse = "|")
has_swords<-str_subset(newdata,match)
shaswords<-head(has_swords)
```

Words containing these: `r shaswords`

